\documentclass[margin, 10.5pt]{res}  
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{paralist}
\usepackage{comment}
\usepackage[dvipsnames]{xcolor}

\newcommand\myshade{85}
\colorlet{mylinkcolor}{blue}
\definecolor{chestnut}{rgb}{0.8, 0.36, 0.36}
\newcommand{\marios}[1]{\textcolor{chestnut}{Marios: #1}}
\hypersetup{
  linkcolor  = mylinkcolor!\myshade!black,
  citecolor  = mylinkcolor!\myshade!black,
  urlcolor   = mylinkcolor!\myshade!black,
  colorlinks = true,
}



\usepackage{helvet}
\newcommand{\field}[2]{\noindent \textbf{#1} \hfill #2 \\}
\newcommand{\uf}[2]{\noindent \textbf{#1} \hfill \url{#2} \\}
\newcommand{\uff}[2]{\item[--] #1 \\ \url{#2}}

% Increase text height
\textheight=680pt

\begin{document}

%------------------------------------X-------------------------------------------
%    NAME AND ADDRESS SECTION
%-------------------------------------------------------------------------------
\name{\textsc{Spyridon Pavlatos}}

% Note that addresses can be used for other contact information:
% -phone numbers
% -email addresses
% -linked-in profile

%\address{\textsc{GitHub}: \href{http://github.com/papachristoumarios}{\nolinkurl{papachristoumarios}}

%\textsc{Address: Archadjikaki 5, Athens, Greece, 17237 }

\address{\textsc{email}: \url{spyrospavlatos4@gmail.com}  \\  \textsc{Linkedin}:  \href{https://www.linkedin.com/in/spyridon-pavlatos/}{spyridon-pavlatos}\\ \textsc{Github}: \href{https://github.com/spyrospav}{spyrospav} \\ \textsc{Mobile:} (+1) (215)980-7610  \\ \textsc{Website:} \href{https://seas.upenn.edu./~pavlatos}{spyrospav.github.io}
}

% Uncomment to add a third address
%\address{Address 3 line 1\\Address 3 line 2\\Address 3 line 3}
%-------------------------------------------------------------------------------


\begin{resume}


\section{Education}

\field{University of Pennsylvania}  {\emph{2022--Present}} 
Ph.D. Computer Science
\begin{compactitem}
\item[--] \emph{Advisor:} Rajeev Alur
\item[--] \emph{Research Focus:} Verification for Distributed Systems
\end{compactitem}
 
\field{National Technical University of Athens}  {\emph{2016--2022}} 
Integrated Masters (5-year joint degree, 300 ECTS) Electrical \& Computer Engineering (ECE)
\begin{compactitem}
\item[--] \emph{Overall GPA:} 9.26/10 
\item[--] \emph{Major:} Computer Science 
\item[--] \emph{Thesis:} \href{http://artemis.cslab.ece.ntua.gr:8080/jspui/bitstream/123456789/18415/1/thesis.pdf}{``A Test Suite for Model Checking Persistent Memory Programs''}. \emph{Advisor:} Kostis Sagonas.
\end{compactitem} 

\begin{comment}
\section{Research \\ Experience}

\textbf{Business Analytics Lab (Undergraduate Researcher)} \hfill \emph{August 2018 --}
\begin{compactitem}
\item[--] Conduct research on Machine Learning on Software Engineering
\begin{compactitem}
\item Source Code Embeddings
\item Software Clustering
\item Layering Violations
\end{compactitem}
\item[--] Research funded by the \textsc{Crossminer} project, supported by \emph{Horizon 2020} grant
\item[--] Research Advisor: Prof. Diomidis Spinellis
\end{compactitem}
\end{comment}

\section{Projects}

\textbf{\href{https://whitenoise.gr/}{White Noise} - Space Engineering Team} \hfill \emph{2017-2019}
\begin{compactitem}
\item[--] Founding member
\item[--] Competed in space engineering competitions for university students:
\begin{compactitem}
\item \textit{Cansat in Greece 2018}. Designed parts of electrical and sensors subsystems. Responsible for social media.
\item \textit{Cansat Competition 2019} by American Astronautical Society. Designed telecommunications and data handling subsystems.
\end{compactitem}
\end{compactitem}

\section{Teaching \\ Experience}

\field{Lab Assistant}{\emph{Spring 2021}}
Institution: National Technical University of Athens \\
Course: \textit{Programming Techniques} \\
Professors: G. Goumas, A. Pagourtzis, N. Papaspyrou

\field{Lab Assistant}{\emph{Fall 2020}}
Institution: National Technical University of Athens \\
Course: \textit{Introduction to Programming} \\
Professors: D. Fotakis, N. Papaspyrou


\section{Technical \\ Skills}

\field{Programming Languages}  {C/C++, Erlang, Haskell, JavaScript, Python, SML, Coq} 
\field{Operating Systems} {Windows, Linux} 
\field{Databases} {MySQL, MongoDB}
\field{Version Control} {Git/Github}
\field{Frameworks \& Tools} {OpenMP, matplotlib, NumPy, Pytorch, LLVM, \textsc{PropEr}}
\field{Typesetting} {\LaTeX}


\section{Honors \& \\ Awards} 
\begin{compactitem}
    \item[--] \emph{Soloman M. Swaab Fellowship} - University of Pennsylvania.
	\item[--] Space Engineering Competition \emph{Cansat in Greece 2018}. 1st Prize in university students category.
    \item[--] Programming Competition \emph{IEEEXtreme 15.0}. Ranked 94\textsuperscript{th} out of 5500+ teams worldwide.
    \item[--] Programming Competition \emph{IEEEXtreme 14.0}. Ranked 99\textsuperscript{th} out of 3700+ teams worldwide.
    \item[--] Programming Competition \emph{IEEEXtreme 13.0}. Ranked 184\textsuperscript{th} out of 4000+ teams worldwide.
    \item[--] Panhellenic Physics Competition \emph{"Aristotle" 2016}. 3rd Prize of Excellence (Bronze Medal). Ranked 25\textsuperscript{th} overall.

\end{compactitem}


\section{Languages} Greek (native), English (C2), German (C1)

\section{Memberships} IEEE Member

\begin{comment}
\section{References \\ available \\ upon request}

Nectarios Koziris \hfill (Prof. at NTUA, \texttt{nkoziris@cslab.ece.ntua.gr)} \\

\end{comment}

\section{Hobbies}
Basketball, Running, Swimming, Cinema, Reading

%\section{Last Updated} \today

\begin{comment}
\section{Links} 

\begin{compactitem}
    \uff{School Curriculum} {https://www.ece.ntua.gr/media/595/odigos_proptyxiakwn_spoydwn.pdf}
    \uff{GitHub Profile} {https://github.com/spyrospav}
    %\uff{}
\end{compactitem}
\end{comment}

\end{resume}
\(\)\end{document}
